Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2015-01-02 wearables_survey.tex
commiting changes only to the .text file.. oops sorry serge

\begin{table}%[h]
\begin{center}
\begin{tabular}{llll}
Recipients	& Chi^2 &	2-tail P &  Effect Size \\
Work-App	& 564.318 & <0.0001 & 0.111\\
Public-App	& 479.980 & <0.0001 &  0.092\\
Friends-App & 380.000 & <0.0001 & 0.075\\
Friends-Work & 20.365 & <0.0001 &  0.004\\
Friends-Public & 5.349 & 0.0207 &  0.001\\
Work-Public&  5.054 & 0.0246 &  0.001\\
\end{tabular}
\caption{Results of a Chi-Squared test of the effects of various recipients contributing to VUR.}
\label{recipient}
\end{center}
\end{table}

@@

  (cubetastic upset rate | smartphone upset rate)\\
Q1: (14.81\% | 6.13\%)\\
Q2: (44.11\% | 19.85\%)\\
Q3: (87.09\% | 58.44\%)\\
Q4: (52.77\% | 55.79\%)\\
Q5: (86.49\% | 91.82\%)\\

			Chi\^2	2-tail p	Sig?		n		effect size\\
Between-All	2.814	0.1395	No		3589		0.001\\
Between-Q1	2.500	0.1139	No		714		0.004\\
Between-Q2	17.333	<0.0001	Yes		708		0.024\\
Between-Q3	0.020	0.8886	No		699		0.000\\
Between-Q4	1.426	0.2324	No		731		0.002\\
Between-Q5	1.611		0.2043	No		710		0.002\\

			Chi\^2	2-tail p	Sig?	Odds ratio	Confidence	Odds range\\
Within-All		0.444	0.505	No	0.5		95\%			0.081 to 2.341\\
Within-Q1		0		1		No	n/a	         n/a	                  n/a\\
Within-Q2		0		1		No	0.5		95\%	                  0.008 to9.605\\
Within-Q3		0		1		No	n/a	         n/a	                  n/a\\
Within-Q4		0		1		No	0.5		95\%			0.008 to9.605\\
Within-Q5		0		1		No	n/a	         n/a	                  n/a\\

>>>>

\begin{table}%[h]
\begin{center}
\begin{tabular}{llll}
Recipients	& Chi^2 &	2-tail P &  Effect Size \\
Work-App	& 564.318 & <0.0001 & 0.111\\
Public-App	& 479.980 & <0.0001 &  0.092\\
Friends-App & 380.000 & <0.0001 & 0.075\\
Friends-Work & 20.365 & <0.0001 &  0.004\\
Friends-Public & 5.349 & 0.0207 &  0.001\\
Work-Public&  5.054 & 0.0246 &  0.001\\
\end{tabular}
\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
\label{recipient}
\end{center}
\end{table}

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{ll}
  (cubetastic upset rate | smartphone upset rate)\\
Q1: (14.81\% | 6.13\%)\\
Q2: (44.11\% | 19.85\%)\\
Q3: (87.09\% | 58.44\%)\\
Q4: (52.77\% | 55.79\%)\\
Q5: (86.49\% | 91.82\%)\\ 
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{deviceVUR}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{llll}
%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
%All	2.814	0.1395	No		3589		0.001\\
%Q1	2.500	0.1139	No		714		0.004\\
%Q2	17.333	<0.0001	Yes		708		0.024\\
%Q3	0.020	0.8886	No		699		0.000\\
%Q4	1.426	0.2324	No		731		0.002\\
%Q5	1.611		0.2043	No		710		0.002\\
Question & Chi^2 &	2-tail P & Effect Size\\
All & 2.814 & 0.1395 & 0.001\\
Q1 & 2.500 & 0.1139 & 0.004\\
Q2 & 17.333 & <0.0001 & 0.024\\
Q3 & 0.020 & 0.8886 & 0.000\\
Q4 & 1.426 & 0.2324 & 0.002\\
Q5 & 1.611	 & 0.2043 & 0.002\\
\end{tabular}
\caption{Results of the effects of <device> type contributing to VUR. Values are Chi-Square test results for between-subjects comparisons for participants who received one question, but not the other.}
\label{betweendevice}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{llll}
%Question & Chi^2 &	2-tail P & Sig? & Odds ratio	 & Confidence& Odds range\\
%All		0.444	0.505	No	0.5		95\%			0.081 to 2.341\\
%Q1		0		1		No	n/a	         n/a	                  n/a\\
%Q2		0		1		No	0.5		95\%	                  0.008 to9.605\\
%Q3		0		1		No	n/a	         n/a	                  n/a\\
%Q4		0		1		No	0.5		95\%			0.008 to9.605\\
%Q5		0		1		No	n/a	         n/a	                  n/a\\
Question & Chi^2 &	2-tail P & Effect Size \\
All & 0.444  & 0.505 & 0.006\\
Q1 & 0 & 1 & 0 \\
Q2 & 0 & 1 & 0\\
Q3 & 0 & 1 & 0\\
Q4 & 0 & 1 & 0\\
Q5 & 0 & 1 & 0\\
\end{tabular}
\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
\label{withindevice}
\end{center}
\end{table}
